---
name: Elad
surname: Oz-Cohen
phone: 054-2121084
email: eladozcohen@gmail.com
linkedin: elad-oz-cohen
github: EladOzCohen
www: eladozcohen.com
date: "February 2023"
output: 
  vitae::awesomecv
---

```{=tex}
\vspace{2mm}
\vspace{2mm}
```
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, 
                      warning = FALSE, message = FALSE,
                      results = "markup")

# Packages #
pacman::p_load(vitae, tidyverse, kableExtra)

# Data #
data <- readxl::read_excel("template.xlsx") %>% 
  group_by(ID) %>% 
  mutate(Why = strsplit(Why, split="\r\n")) %>% 
  ungroup
```

# Skills

**Software**: SQL, Tableau, R, Python, Excel.\
**Languages**: Hebrew (native), English (fluent).



# moreSkills
```{r}
data %>% 
  filter(Section=="Projects1") %>% 
  detailed_entries(what = Why) 
```
[*Webpage*](https://eladoz.shinyapps.io/Mean_and_Median_Manipulation/)



# Projects

\vspace{2mm}

-   Programmed an interactive web application that explores the behavior of various measurements of central tendencies. [*Webpage*](https://eladoz.shinyapps.io/Mean_and_Median_Manipulation/)

-   Data Analysis: Data Exploration and insights extraction via SQL and Tableau. [*Webpage*](https://EladOzCohen.github.io/Projects.html)

-   Data Visualization: Collection of assorted ongoing data visualizations. [*Webpage*](https://EladOzCohen.github.io/Visualizations.html)

\vspace{2mm}

# Education

```{r}
data %>%  #The string behind this box gives the title for this section.
          # What = 2nd hearder
          # with = 1st header
          # Section = in the xlsx file, tells R which lines to take the data from.
  filter(Section=="Education and Professional Development") %>% 
  detailed_entries(what = With, When, with = What, Where, Why)
```

# Experience

```{r}
data %>% 
  filter(Section=="Professional Experience") %>% 
  detailed_entries(what = With, When, with = What, Where, Why)
```

\vspace{2mm}

\vspace{1.75mm}
